notes

### 2023-02-28 paper/article.Rnw
witp
notes

\subsection{Small area estimation} 
Small area estimation (SAE) is a collection of methods that are aimed at
estimating subpopulation parameters in cases where there the number of
observations in a subpopulation is so mall that direct estimation leads to
unacceptable estimation variance. Instead one resorts to indirect estimation,
meaning that one estimates the parameter for a larger subpopulation that
includes the target subpopulation. This estimate is then interpreted as an
estimate for the target subpopulation. Here, we shall be interested in
estimating the average turnover from industrial activities (\code{industrial})
by SBI and size class.

@@

$R = \{\}$\;
\For{$a\in A$}{
  $i=0$ \tcp*{Initiate collapse level}
  $d = f^*(\{a\})$ \tcp*{Get subset of $U$}
  \While{$i<n \land \lnot\beta(d)$}{ \label{line:while}
    $i = i+1$ \tcp*{Increase collapse level} 
    $d = (f^*\circ F_i^*\circ F_i)(a)$ \tcp*{Collapse and get subset}
  }\label{line:endwhile}
  \If{$i<n \lor \beta(d)$}{ \label{line:cond}
    $R = R\cup \{(a, i,\phi(d))\}$\;
  } 
}

@@

Comparing Algorithms~\ref{alg:sac} and~\ref{alg:saccg}, we see that the
standard split-apply-combine algorithm has worst-case runtime complexity
$O(|A|)$, which is equal to the best case $\Omega(|A|)$. The
split-apply-combine with collapsing groups algorithm has best case
$\Omega(|A|)$ equal to standard split-apply-combine but worst case $O(n|A|)$.
In fact, the best case for Algorithm~\ref{alg:saccg} is achieved by setting
$\beta:d\mapsto\texttt{True}$. It is not hard to see that in this case
Algorithm~\ref{alg:saccg} reduces to Algorithm~\ref{alg:sac}. The worst case is
achieved by setting $\beta: d\mapsto \texttt{False}$.

>>>>

\subsection{Small area estimation} 
Small area estimation (SAE) is a collection of methods that are aimed at
estimating subpopulation parameters in cases where there the number of
observations in a subpopulation is so mall that direct estimation leads to
unacceptable estimation variance. Instead one resorts to indirect estimation,
meaning that one estimates parameters for a larger subpopulation which are then
used in the estimate for the target subpopulation.  Here, we shall be
interested in estimating the average turnover from industrial activities
(\code{industrial}) by SBI and size class.

@@

$R = \{\}$\;
\For{$a\in A$}{
  $i=0$ \tcp*{Initiate collapse level}
  $d = f^*(\{a\})$ \tcp*{Get subset of $U$}
  \While{$i<n \land \lnot\beta(d)$}{ \label{line:while}
    $i = i+1$ \tcp*{Increase collapse level} 
    $d = (f^*\circ F_i^*\circ F_i)(a)$ \tcp*{Collapse and get subset}
  }\label{line:endwhile}
  \If{$i<n \lor \beta(d)$}{ \label{line:cond}
    $R = R\cup \{(a, i,\phi(d))\}$\; \label{line:R}
  } 
}

@@

Comparing Algorithms~\ref{alg:sac} and~\ref{alg:saccg}, we see that the
standard split-apply-combine algorithm has worst-case runtime complexity
$O(|A|)$, which is equal to the best case $\Omega(|A|)$. The
split-apply-combine with collapsing groups algorithm has best case
$\Omega(|A|)$ equal to standard split-apply-combine but worst case $O(n|A|)$.
In fact, the best case for Algorithm~\ref{alg:saccg} is achieved by setting
$\beta:d\mapsto\texttt{True}$. It is not hard to see that in this case
Algorithm~\ref{alg:saccg} reduces to Algorithm~\ref{alg:sac}. The worst case is
achieved by setting $\beta: d\mapsto \texttt{False}$. In that case the while
loop in Line~\ref{line:while} is iterated $n-1$ times (yielding total $n$
executions of $f^*$) while Line~\ref{line:R} is never executed.

### 2023-02-28 paper/notes/notes.tex
notes

If we assume the approximation $n_L/\frac{\mathbb{E}(n_L}\approx 1$ we 
get
$$
\hat{\mu}^{\textrm{BARE}}_{Y|i}(L)\approx \bar{y}_L.
$$

>>>>

If we assume the approximation $n_L/\mathbb{E}(n_L)\approx 1$ we get
$$
\hat{\mu}^{\textrm{BARE}}_{Y|i}(L)\approx \bar{y}_L.
$$
Note that in the limit where $L=\{1,2,\ldots M\}$, i.e. the case where $S_L$
equals the full sample $S$, the approximation becomes an equality. It is not in
true in general that the approximation improves when $L$ is increased.
